### 2012-05-09 Rctl/inst/doc/manual.Rnw
[User Manual] Updates

\textbf{\sffamily Abstract}: Introduction into quanitative correlation 
locus (CTL) mapping using the R package CTL
\vfill

@@

Loading your data

@@

@@

\newpage
{\small
\noindent \textbf{\sffamily Package CTL function overview} \\
\noindent \begin{tabular}{ll} 
\hspace*{25mm} & \hspace*{103mm} \\ \hline
CTLscan & Genome wide scan for CTL \\
CTLscan.network & Scan for CTL using start gene(s) \\
CTLpermute & Significance thresholds for CTL by permutation \\
plot & Plot CTL profiles at increasing cut-offs \\
image & Image a multiple phenotype scan \\
\hline
\end{tabular}
}

>>>>

\textbf{\sffamily Abstract}: Introduction into quanitative correlation locus (CTL) mapping using 
the R package 'ctl'
\vfill

@@

\emph{Loading your Excel / CSV data}
Use the example excel file and simply replace the example data by your own then: 
  $$File->Save As->TODO$$

After you have stored the data as plain text open the files in a text editor (NOT WORD, for 
windows Notepad++ is a good option) and check to see if your data is stored correctly, if 
not reformat your data in both the genotype.csv and the phenotype.csv files to match the 
following:

<<echo=TRUE,eval=FALSE>>=
setwd("<PATH_TO_DATA>")
genotypes <- read.csv("genotypes.csv",row.names=1,col.names=TRUE)
phenotypes <- read.csv("phenotypes.csv",row.names=1,col.names=TRUE)
ctls <- CTLscan(genotypes, phenotypes)
@

\emph{Use an R/qtl formatted dataset}
Provided is the main interface functions to R/qtl: $CTLscan.cross()$ this functions accepts and 
R/qtl formatted cross object as input and will scan CTL, perform permutations and transform the
detected differential correlation to LOD score matrices.
As an example we show the code to scan the multitrait dataset provided in R/qtl:

<<echo=TRUE,eval=FALSE>>=
require(qtl)        #load the R/qtl package
data(multitrait)    #load the dataset
ctls <- CTLscan.cross(multitrait, pheno.col=1:2)
@

@@

\emph{CTLscan options}
The genotype matrix and the $geno.enc$ param, the phenotype matrix, the important $n.perms$ param, 
which should be set to as many as possible, especially when publishing any results, but for a quick 
scan 100 is ussualy sufficient.

When experimental setups are more complex a user can supply QTL results via the $have.qtl$ option.

<<echo=TRUE,eval=FALSE>>=
require(qtl)        #load the R/qtl package
data(multitrait)    #load the dataset
qtls <- scanone(multitrait, pheno.col=1:24)[,-c(1,2)]
ctls <- CTLscan.cross(multitrait, pheno.col=1:2, have.qtl=qtls)
@

, when no qtls are supplied the internal QTL mapping routine is used, which can deal with just a 
single condition per individual. An environmental condition can be specified by the $conditions$ 
param and are also passed to the internal QTL mapping algorithm.

<<echo=TRUE,eval=FALSE>>=
#Specify that individuals 1:81 were in condition A / e.g. treatment
#Specify that individuals 82:162 were in condition B / e.g. control
conditions <- c(rep(1,81),rep(2,81))
ctls <- CTLscan(ath.metab$genotypes, ath.metab$phenotypes, conditions=)
@

\bigskip
\textbf{\sffamily Big data and Dctl}
\nopagebreak

Explains how to use the D version to map big datsets

@@

\newpage
{\small
\noindent \textbf{\sffamily Package CTL function overview} \\
\noindent \begin{tabular}{ll} 
\hspace*{25mm} & \hspace*{103mm} \\ \hline
CTLscan & Main function for Genome wide scan for Correlated Trait Loci \\
CTLscan.network & Scan only a subset of traits for CTL using start gene(s) \\
CTLpermute & Significance thresholds for CTL by permutation\\
plot & Plot CTL profiles at increasing cut-offs \\
image & Image a multiple phenotype scan \\
\hline
\end{tabular}
}
